I write to you to apply for writing my Master thesis at Intel. The announced position looks interesting and seems like something I can see myself working with in the future.

I am a high-achieving university student with a passion for programming and I have always taken an active interest in technology. I was first introduced to programming at age 14 after which I taught myself the basics of C\texttt{++} and Java.

I have tailored my university education to be able to write as much code as possible and to try out many different programming languages. I have studied topics like advanced algorithm design, real-time programming and computer security, as well as assembler coding and natural language processing using regular expressions. I recently took a course in functional programming which really opened my eyes to the different ways of solving complex problems.

I am very interested in mathematics and have always excelled academically in the subject. I have knowledge in areas like algebra, calculus, statistics, numerical analysis and topology. I have been a Linux user for many years, I am comfortable with working in the terminal and I enjoy writing my own scripts.

I am a self-starter who likes personal responsibility, and I take pride in writing clear and effective code. I know how to work independently – how to search for information on my own – as well as working within a group. I am a social person that thrives in the company of others. I love to travel and would like to pursue an international career at some point.

Thanks for your time, I look forward to hearing back from you soon.
